True versus apparent shapes of astrophysical bow shocks

### 2017-04-18 papers/Paper1/quadrics-appendix.tex
Add big table of stats tests to paper - still needs fixing
Finish tweaks to big table of p-values

>>>>

\clearpage
\sisetup{detect-weight=true, detect-shape=true, detect-inline-weight=math}
\sisetup{round-mode=figures, round-precision=2}
\begin{landscape}
\begin{table}
  \setlength\tabcolsep{2pt}
  \caption{Big table of \(p\)-values}
  \begin{tabular}{@{} ll @{\ } S[round-mode=places]S[round-mode=places] S[round-mode=places]S[round-mode=places] SS SS @{\quad\quad\quad} SSS @{\quad} S@{}S@{}S @{}}\toprule
     & & \multicolumn{2}{c}{Mean} & \multicolumn{2}{c}{Std.\ Dev.} & \multicolumn{2}{c}{Obs.\ Disp.} & \multicolumn{2}{c @{\quad\quad\quad}}{s.e.m.} & \multicolumn{3}{c @{\quad} }{\dotfill Effect sizes\dotfill } & \multicolumn{3}{c}{\dotfill Non-parametric test \(p\)-values  \dotfill} \\ 
    {Comparison} & {Variable} & {\(\langle \text{A} \rangle\)} & {\(\langle \text{B} \rangle\)} & {\(\sigma_{\text{A}}\)} & {\(\sigma_{\text{B}}\)} & {\(\langle \epsilon_{\text{A}} \rangle\)} & {\(\langle \epsilon_{\text{B}} \rangle\)} & {\((\sigma/\!\sqrt n)_{\text{A}}\)} & {\((\sigma/\!\sqrt n)_{\text{B}}\)} & {\(r_b\)} & {\(d_C\)} & {\(\sigma_{\text{A}}/\sigma_{\text{B}}\)} & \multicolumn{1}{c}{Anderson--Darling} & \multicolumn{1}{c}{Rank biserial} &  \multicolumn{1}{c}{Brown--Forsythe}\\
\midrule
    \multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Median split of continuous variables \dotfill}\\
    \addlinespace
    Faint/bright & \(R_{90}\) & 1.677 & 1.768 & 0.269 & 0.316 & 0.231 & 0.236 & 0.025 & 0.030 & \bfseries 0.174 & \bfseries -0.308 & 0.851 & \bfseries 0.0215 & \bfseries 0.0235 & 0.125\\
\(H\) magnitude  & \(\Delta R_{90}\) & 0.183 & 0.198 & 0.161 & 0.163 &  &  & 0.015 & 0.015 & 0.070 & -0.093 & 0.987 & 0.538 & 0.365 & 0.761\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.655 & 1.917 & 0.631 & 1.045 & 0.097 & 0.078 & 0.059 & 0.098 & 0.123 & -0.303 & \bfseries 0.604 & 0.123 & 0.111 & \bfseries 0.0335\\
\addlinespace
Low/high  & \(R_{90}\) & 1.707 & 1.739 & 0.250 & 0.336 & 0.256 & 0.212 & 0.024 & 0.031 & 0.061 & -0.110 & \bfseries 0.745 & \bfseries 0.0281 & 0.428 & \bfseries 0.00139\\
\(R_0\) & \(\Delta R_{90}\) & 0.175 & 0.204 & 0.157 & 0.165 &  &  & 0.015 & 0.015 & 0.091 & -0.176 & 0.948 & 0.103 & 0.238 & 0.193\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.766 & 1.803 & 0.975 & 0.755 & 0.114 & 0.062 & 0.092 & 0.071 & 0.100 & -0.043 & 1.291 & 0.228 & 0.192 & 0.599\\
\addlinespace
Low/high & \(R_{90}\) & 1.703 & 1.742 & 0.267 & 0.323 & 0.233 & 0.235 & 0.025 & 0.030 & 0.040 & -0.132 & 0.824 & 0.554 & 0.602 & 0.123\\
extinction & \(\Delta R_{90}\) & 0.186 & 0.195 & 0.138 & 0.183 &  &  & 0.013 & 0.017 & -0.039 & -0.057 & 0.754 & 0.301 & 0.61 & 0.112\\
\(n_{\text{A}} =  n_{\text{B}} = 113\)  & \(R_{c}\) & 1.725 & 1.846 & 0.822 & 0.917 & 0.091 & 0.085 & 0.077 & 0.086 & 0.082 & -0.139 & 0.896 & 0.219 & 0.285 & 0.982\\
\addlinespace
Low/high & \(R_{90}\) & 1.722 & 1.724 & 0.328 & 0.261 & 0.234 & 0.234 & 0.031 & 0.024 & 0.020 & -0.008 & 1.256 & 0.308 & 0.795 & 0.0534\\
\(\vert{}b\vert\)  & \(\Delta R_{90}\) & 0.188 & 0.191 & 0.161 & 0.162 &  &  & 0.015 & 0.015 & 0.009 & -0.021 & 0.995 & 0.964 & 0.907 & 0.694\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.706 & 1.862 & 0.727 & 0.988 & 0.085 & 0.091 & 0.068 & 0.092 & 0.069 & -0.181 & 0.736 & 0.19 & 0.368 & 0.0842\\
\addlinespace
High/low & \(R_{90}\) & 1.734 & 1.707 & 0.279 & 0.321 & 0.241 & 0.223 & 0.024 & 0.034 & -0.049 & 0.093 & 0.868 & 0.361 & 0.532 & 0.159\\
\(\cos \ell\)  & \(\Delta R_{90}\) & 0.182 & 0.201 & 0.155 & 0.171 &  &  & 0.013 & 0.018 & 0.054 & -0.122 & 0.909 & 0.604 & 0.491 & 0.365\\
\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(R_{c}\) & 1.807 & 1.751 & 0.946 & 0.742 & 0.090 & 0.084 & 0.081 & 0.078 & -0.000 & 0.064 & 1.274 & 1.03 & 0.999 & 0.549\\
\midrule
    \multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Categorical variables \dotfill}\\
    \addlinespace
Environment:  & \(R_{90}\) & 1.735 & 1.693 & 0.283 & 0.338 & 0.238 & 0.218 & 0.022 & 0.053 & -0.070 & 0.142 & 0.838 & 0.603 & 0.49 & 0.392\\
Facing & \(\Delta R_{90}\) & 0.190 & 0.195 & 0.161 & 0.172 &  &  & 0.012 & 0.027 & -0.019 & -0.034 & 0.938 & 0.507 & 0.85 & 0.438\\
\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(R_{c}\) & 1.757 & 1.852 & 0.854 & 0.899 & 0.087 & 0.083 & 0.066 & 0.140 & 0.042 & -0.110 & 0.950 & 0.713 & 0.676 & 0.377\\
\addlinespace
Environment:  & \(R_{90}\) & 1.735 & 1.680 & 0.283 & 0.309 & 0.238 & 0.233 & 0.022 & 0.077 & -0.130 & 0.193 & 0.916 & 0.518 & 0.391 & 0.782\\
\hii & \(\Delta R_{90}\) & 0.190 & 0.175 & 0.161 & 0.138 &  &  & 0.012 & 0.034 & -0.048 & 0.095 & 1.170 & 0.932 & 0.754 & 0.799\\
\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(R_{c}\) & 1.757 & 1.907 & 0.854 & 0.955 & 0.087 & 0.105 & 0.066 & 0.239 & 0.024 & -0.174 & 0.894 & 0.496 & 0.875 & 0.255\\
\addlinespace
Single/multiple & \(R_{90}\) & 1.709 & 1.762 & 0.289 & 0.315 & 0.230 & 0.243 & 0.022 & 0.041 & 0.074 & -0.177 & 0.917 & 0.342 & 0.396 & 0.338\\
source candidate & \(\Delta R_{90}\) & 0.184 & 0.206 & 0.162 & 0.160 &  &  & 0.013 & 0.021 & 0.093 & -0.136 & 1.013 & 0.421 & 0.284 & 0.97\\
\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(R_{c}\) & 1.767 & 1.833 & 0.825 & 0.988 & 0.090 & 0.080 & 0.064 & 0.128 & 0.027 & -0.076 & 0.835 & 0.999 & 0.756 & 0.605\\
\addlinespace
With/without  & \(R_{90}\) & 1.734 & 1.721 & 0.289 & 0.298 & 0.223 & 0.237 & 0.043 & 0.022 & -0.042 & 0.044 & 0.970 & 0.595 & 0.667 & 0.563\\
\SI{8}{\um} emission & \(\Delta R_{90}\) & 0.203 & 0.186 & 0.205 & 0.149 &  &  & 0.031 & 0.011 & 0.021 & 0.106 & 1.377 & 0.765 & 0.826 & 0.219\\
\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(R_{c}\) & 1.714 & 1.802 & 0.598 & 0.926 & 0.091 & 0.087 & 0.089 & 0.069 & -0.012 & -0.101 & 0.646 & 0.824 & 0.904 & 0.2\\
\midrule
    \multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Intercomparison with other datasets \dotfill}\\
    \addlinespace
MIPS vs Orion & \(R_{90}\) & 1.723 & 2.418 & 0.297 & 0.811 &  &  & 0.020 & 0.191 & \bfseries 0.700 & \bfseries -1.928 & \bfseries 0.366 & \bfseries 8.02e-06 & \bfseries 7.84e-07 & \bfseries 6.41e-06\\
 & \(\Delta R_{90}\) & 0.190 & 0.506 & 0.162 & 0.551 &  &  & 0.011 & 0.130 & 0.220 & -1.468 & \bfseries 0.294 & \bfseries 3.6e-05 & 0.121 & \bfseries 4.03e-14\\
\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(R_{c}\) & 1.784 & 2.639 & 0.871 & 1.302 &  &  & 0.058 & 0.307 & \bfseries 0.516 & \bfseries -0.940 & 0.669 & \bfseries 0.000505 & \bfseries 0.000273 & 0.12\\
\addlinespace
MIPS vs RSG & \(R_{90}\) & 1.723 & 1.386 & 0.297 & 0.122 &  &  & 0.020 & 0.046 & \bfseries -0.756 & \bfseries 1.152 & 2.425 & \bfseries 0.000494 & \bfseries 0.000671 & 0.0573\\
 & \(\Delta R_{90}\) & 0.190 & 0.197 & 0.162 & 0.296 &  &  & 0.011 & 0.112 & -0.242 & -0.045 & 0.546 & 0.156 & 0.276 & 0.397\\
\(n_{\text{A}}, n_{\text{B}} = 227, 7\) & \(R_{c}\) & 1.784 & 1.426 & 0.871 & 0.079 &  &  & 0.058 & 0.030 & -0.201 & 0.418 & 10.969 & 0.0742 & 0.367 & 0.0505\\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}
